\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.6in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-.6in}
\addtolength{\textheight}{1.2in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\normalsize
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\footnotesize{#1 \vspace{-2pt}}
}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small#1} & \small#2 \\
      \textit{\footnotesize#3} & \textit{\footnotesize#4} \\
    \end{tabular*}\vspace{-6pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{\small#1} & \footnotesize#2 \\
    \end{tabular*}\vspace{-6pt}
}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4pt}}

%-------------------------------------------
\begin{document}

\begin{center}
    \textbf{\Large \scshape Hardik Bajaj} \vspace{-2pt}\\
    \footnotesize +91-9501855364 $|$
    \href{mailto:Hardikbajaj364@gmail.com}{\underline{Hardikbajaj364@gmail.com}} $|$
    \href{https://www.linkedin.com/in/hardikbajaj364}{\underline{LinkedIn}} $|$
    \href{https://github.com/Hardik364}{\underline{GitHub}}
\end{center}\vspace{-8pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Chitkara University}{Punjab, India}
      {B.Tech Computer Science Engineering}{Aug. 2022 -- June 2026}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Software Development Intern (QA \& Testing)}{July 2025 -- Feb. 2026}
      {Sprouts.ai}{Mohali, India}
      \resumeItemListStart
        \resumeItem{Designed automated test cases for REST APIs using Postman, validating endpoint integrity across staging/production environments.}
        \resumeItem{Collaborated with MERN team on JIRA, logging and verifying bug fixes in Agile sprint cycles.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \footnotesize{\item{
        \textbf{Languages:} JavaScript, TypeScript, HTML5, CSS3, SQL \quad \textbf{Frontend:} Next.js, React.js, Tailwind CSS, Framer Motion \\
        \textbf{Backend:} Node.js, Express.js, Socket.IO, REST APIs, JWT Auth \quad \textbf{Databases:} PostgreSQL, Redis, MongoDB, Firebase \\
        \textbf{Real-time:} WebRTC, Web Push API, Service Workers \quad \textbf{Tools:} Git, GitHub, Postman, Vercel, Render, PM2
    }}
\end{itemize}\vspace{-4pt}

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

    \resumeProjectHeading
      {\textbf{OpenChat} $|$ \emph{Next.js 15, Node.js, Express.js, PostgreSQL, Redis, Socket.IO, WebRTC}}{2025 -- Present}
      \resumeItemListStart
        \resumeItem{Full-stack real-time peer-to-peer voice calling platform for college students with JWT auth, Google OAuth2, and Redis-backed session management supporting 1,200+ concurrent users.}
        \resumeItem{Backend: Node.js, Express.js, Socket.IO for matching and signaling. Frontend: Next.js 15, Tailwind CSS v4, WebRTC with Perfect Negotiation, Web Push API. Deployed on Vercel/Render.}
        \resumeItem{PostgreSQL (Neon), Redis (Upstash), PM2 process management — achieving sub-100ms WebSocket latency and 99.9\% uptime with Helmet security middleware.}
        \resumeItem{\href{https://unibuddy-nu.vercel.app/signup}{\underline{unibuddy-nu.vercel.app}}}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{FlexItOut} $|$ \emph{Next.js, React.js, TensorFlow.js, Express.js, PostgreSQL}}{Feb. 2025 -- Mar. 2025}
      \resumeItemListStart
        \resumeItem{Full-stack AI fitness app with client-side real-time pose detection using TensorFlow.js MoveNet, rep counting, form accuracy scoring for Push-ups, Squats, Crunches.}
        \resumeItem{Node.js/Express.js backend with Firebase Auth and PostgreSQL; responsive React dashboard with live pose skeleton overlay and progress analytics. Deployed on Vercel.}
        \resumeItem{\href{https://flex-it-out-drab.vercel.app/}{\underline{flex-it-out.vercel.app}}}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Hardik Portfolio} $|$ \emph{Next.js 14, TypeScript, Tailwind CSS, Framer Motion}}{Mar. 2026 -- Present}
      \resumeItemListStart
        \resumeItem{Modern responsive portfolio with smooth animations, project showcases, resume download, and social integrations. Deployed on Vercel with 95+ Lighthouse score.}
        \resumeItem{\href{https://hardik-portfolio-steel.vercel.app/}{\underline{hardik-portfolio-steel.vercel.app}}}
      \resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}
