\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{{#1 \vspace{-2pt}}}
}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
\begin{document}

\begin{center}
    \textbf{\Huge \scshape Hardik Bajaj} \\ \vspace{1pt}
    \small +91-9501855364 $|$
    \href{mailto:Hardikbajaj364@gmail.com}{\underline{Hardikbajaj364@gmail.com}} $|$
    \href{https://www.linkedin.com/in/hardikbajaj364}{\underline{linkedin.com/in/hardikbajaj364}} $|$
    \href{https://github.com/Hardik364}{\underline{github.com/Hardik364}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Chitkara University}{Punjab, India}
      {Bachelor of Computer Science Engineering}{Aug. 2022 -- June 2026}
    \resumeSubheading
      {Deakin University (Exchange Program)}{Burwood, Melbourne}
      {Bachelor of Computer Science Engineering}{Aug. 2022 -- June 2024}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Software Development Intern (QA \& Testing)}{July 2025 -- Feb. 2026}
      {Sprouts.ai}{Mohali, India}
      \resumeItemListStart
        \resumeItem{Designed and executed manual and automated test cases for REST APIs using Postman, validating request/response integrity and ensuring correctness of full-stack web application endpoints across staging and production environments.}
        \resumeItem{Collaborated with the MERN stack development team on JIRA to log, track, and verify bug fixes, gaining hands-on exposure to Agile sprint cycles, code reviews, and release pipelines.}
        \resumeItem{Identified edge cases and regression issues across front-end and back-end modules, contributing to a measurable reduction in post-release bug reports and improving overall product quality.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
        \textbf{Languages:}{ JavaScript (ES6+), TypeScript, Java, HTML5, CSS3, SQL} \\
        \textbf{Frontend:}{ Next.js, React.js, Tailwind CSS, Framer Motion, Web APIs} \\
        \textbf{Backend:}{ Node.js, Express.js, Socket.IO, REST APIs, JWT Authentication} \\
        \textbf{Databases:}{ PostgreSQL, Redis, MongoDB, Firebase Firestore, NoSQL} \\
        \textbf{Real-time:}{ WebRTC, Socket.IO, Web Push API, Service Workers} \\
        \textbf{Developer Tools:}{ Git, GitHub, Postman, VS Code, JIRA, Vercel, Render, PM2} \\
        \textbf{Concepts:}{ Full-Stack Development, Microservices, JWT Auth, OAuth2, Responsive Design, Agile/Scrum} \\
    }}
\end{itemize}

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

    \resumeProjectHeading
      {\textbf{OpenChat} $|$ \emph{Next.js 15, Node.js, Express.js, PostgreSQL, Redis, Socket.IO, WebRTC}}{Jan. 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Engineered a full-stack real-time communication platform connecting college students across India with encrypted peer-to-peer voice calls, real-time messaging, and community forums — supporting 1,200+ concurrent active users.}
        \resumeItem{Built scalable real-time backend with Node.js, Express.js, and Socket.IO (WebSocket) for live matching algorithms, call signaling, and message delivery; implemented JWT authentication (7-day TTL for users, 24h for guests) with Google OAuth2 integration via `google-auth-library`.}
        \resumeItem{Designed high-performance frontend with Next.js 15 App Router and Tailwind CSS v4, integrated WebRTC with Perfect Negotiation pattern for peer-to-peer calls, implemented Web Push API for notifications, and leveraged Upstash Redis for distributed session management, rate limiting, and shadow banning.}
        \resumeItem{Deployed PostgreSQL (Neon serverless), Redis (Upstash), and Node.js backend on Render; frontend on Vercel — achieving sub-100ms WebSocket latency and 99.9\% uptime with PM2 process management and Helmet security middleware.}
        \resumeItem{\href{https://unibuddy-nu.vercel.app/signup}{\underline{unibuddy-nu.vercel.app}}}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{FlexItOut} $|$ \emph{Next.js, React.js, Node.js, Express.js, PostgreSQL, TensorFlow.js}}{Feb. 2025 -- Mar. 2025}
      \resumeItemListStart
        \resumeItem{Developed a full-stack MERN AI fitness web application at the Bajaj Finserv Health Hackathon, featuring real-time pose detection, rep counting, and live form feedback using TensorFlow.js MoveNet — running entirely client-side for zero backend inference latency.}
        \resumeItem{Built scalable RESTful APIs with Node.js and Express.js to manage user profiles, workout history, and exercise plans, backed by PostgreSQL; integrated Firebase Authentication for secure sign-in and session management.}
        \resumeItem{Designed a responsive React.js dashboard with live pose skeleton overlay, rep counter, form accuracy scoring, and progress analytics — supporting Push-ups, Squats, and Crunches with angle-based form detection.}
        \resumeItem{\href{https://flex-it-out-drab.vercel.app/}{\underline{flex-it-out.vercel.app}}}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Hardik Portfolio} $|$ \emph{Next.js 14, React.js, TypeScript, Tailwind CSS, Framer Motion}}{Mar. 2026 -- Present}
      \resumeItemListStart
        \resumeItem{Built a modern, fully responsive portfolio website showcasing projects, skills, and technical experience — optimized for performance with Next.js 14 server-side rendering and static generation.}
        \resumeItem{Implemented smooth scroll animations, project showcases, contact form, resume download, and social integrations (GitHub, LinkedIn) using Framer Motion for engaging user interactions and modern UI patterns.}
        \resumeItem{Deployed on Vercel with automatic CI/CD from GitHub, achieving 95+ Lighthouse score, mobile-first design, and sub-1s load times across all pages.}
        \resumeItem{\href{https://hardik-portfolio-steel.vercel.app/}{\underline{hardik-portfolio-steel.vercel.app}}}
      \resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}
